---
title: "RentMasseur Bio Analysis Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: bootstrap
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(dplyr)
library(plotly)
library(jsonlite)
library(DT)
library(knitr)
library(scales)

# Load data
load_data <- function() {
  # Try to load JSON data
  tryCatch({
    json_data <- fromJSON("data/masseur_profiles.json")
    df <- as.data.frame(t(json_data))
    return(df)
  }, error = function(e) {
    # Fallback to CSV
    tryCatch({
      df <- read.csv("data/masseur_profiles.csv", stringsAsFactors = FALSE)
      return(df)
    }, error = function(e) {
      return(NULL)
    })
  })
}

df <- load_data()

# Process data
if (!is.null(df)) {
  df$has_bio <- ifelse(nchar(as.character(df$bio)) > 10, "Yes", "No")
  df$bio_length <- nchar(as.character(df$bio))
  df$last_updated <- as.character(df$last_updated)
}
```

Column {data-width=350}
-----------------------------------------------------------------------

### Overview

```{r}
if (!is.null(df)) {
  total_profiles <- nrow(df)
  profiles_with_bio <- sum(df$has_bio == "Yes")
  profiles_without_bio <- sum(df$has_bio == "No")
  
  valueBox(total_profiles, 
           icon = "fa-users",
           caption = "Total Profiles",
           color = "primary")
}
```

### Bio Coverage

```{r}
if (!is.null(df)) {
  bio_pct <- round((profiles_with_bio / total_profiles) * 100, 1)
  
  valueBox(bio_pct, 
           icon = "fa-file-text",
           caption = "% with Bio Content",
           color = ifelse(bio_pct > 50, "success", "warning"))
}
```

### Data Status

```{r}
if (!is.null(df)) {
  has_views <- sum(df$total_views > 0, na.rm = TRUE)
  has_reg_date <- sum(df$registration_date != "", na.rm = TRUE)
  
  valueBox(has_views, 
           icon = "fa-eye",
           caption = "Profiles with View Data",
           color = "info")
}
```

### Key Findings

**Data Limitations:**
- CrowdSec captcha protection blocks automated data collection
- View counts are placeholder values (999)
- Registration dates not available
- Only 1 profile has bio content (auto-generated)

**Recommendations:**
- Manual data collection required for real analysis
- Use karpathianwolf bio template as best practice
- Emphasize 24/7 availability in bios
- Include professional credentials and call-to-action

Column {data-width=650}
-----------------------------------------------------------------------

### Profile Rankings

```{r}
if (!is.null(df)) {
  DT::datatable(df %>%
                select(username, total_views, views_per_day, location, has_bio, bio_length) %>%
                arrange(desc(total_views)),
              options = list(pageLength = 10),
              colnames = c("Username", "Total Views", "Views/Day", "Location", "Has Bio", "Bio Length"))
}
```

### Bio Status Distribution

```{r}
if (!is.null(df)) {
  bio_status <- data.frame(
    Status = c("With Bio", "Without Bio"),
    Count = c(profiles_with_bio, profiles_without_bio)
  )
  
  p <- ggplot(bio_status, aes(x = Status, y = Count, fill = Status)) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = c("With Bio" = "#2ecc71", "Without Bio" = "#e74c3c")) +
    labs(title = "Bio Content Coverage",
         x = "Bio Status",
         y = "Number of Profiles") +
    theme_minimal() +
    theme(legend.position = "none")
  
  ggplotly(p)
}
```

### Bio Length Analysis

```{r}
if (!is.null(df) && profiles_with_bio > 0) {
  bio_df <- df %>% filter(bio_length > 0)
  
  p <- ggplot(bio_df, aes(x = username, y = bio_length, fill = has_bio)) +
    geom_bar(stat = "identity") +
    coord_flip() +
    labs(title = "Bio Length by Profile",
         x = "Username",
         y = "Bio Length (characters)") +
    theme_minimal()
  
  ggplotly(p)
} else {
  cat("No bio data available for visualization")
}
```

Column
-----------------------------------------------------------------------

### Bio Best Practices

**High-Performing Bio Characteristics:**

1. **Availability**
   - "Available 24/7" or "Flexible scheduling"
   - Same-day availability mentions
   - Weekend/holiday availability

2. **Experience**
   - Specific training/certifications
   - Years of experience
   - Specialized techniques

3. **Benefits**
   - Pain relief, stress reduction
   - Wellness and relaxation focus
   - Customized approach

4. **Length**
   - Medium length (200-400 characters)
   - Long enough to convey value
   - Short enough to be read quickly

5. **Urgency**
   - Call-to-action phrases
   - Contact information
   - Booking encouragement

### karpathianwolf Bio Analysis

**Current Bio Metrics:**
- Length: 988 characters (very long)
- Words: 136
- Sentences: 8
- Availability mentions: 4
- Specialty mentions: 3
- Benefit mentions: 2

**Strengths:**
- ✅ 24/7 availability clearly stated
- ✅ Multiple availability options
- ✅ Professional experience mentioned
- ✅ Specialties listed
- ✅ Call-to-action included

**Potential Improvements:**
- 📈 Add specific years of experience
- 📈 Include certification details
- 📈 Add client testimonials/reviews
- 📈 Mention specific techniques offered
- 📈 Include pricing or special offers

### Methodology

**Data Collection:**
- C++ scraper with libcurl
- Targeted 19 known profiles
- Attempted login with credentials
- Blocked by CrowdSec captcha

**Analysis Framework:**
- Bio keyword analysis
- Length optimization
- Availability messaging
- Experience credentials
- Call-to-action effectiveness

**Limitations:**
- Automated scraping blocked by security
- Manual data collection required
- Placeholder data used for demonstration
- Real engagement metrics unavailable

### Next Steps

**To Get Real Data:**
1. Manual profile visits with captcha solving
2. Record actual view counts
3. Note registration dates
4. Copy bio content

**To Improve Analysis:**
1. A/B test different bio variations
2. Track view changes over time
3. Correlate bio features with engagement
4. Identify top-performing patterns

**To Optimize Your Profile:**
1. Use karpathianwolf bio template
2. Emphasize 24/7 availability
3. Add professional credentials
4. Include clear call-to-action
5. Monitor and iterate based on results
